Garbage Collection Evaluation Infrastructure\\ for the Cog VM

### 2018-06-20 paper.tex
Minor edits

We built three benchmarks out of the potential configurations:
\begin{itemize}
\item \emph{FragmentedHeap:} First, objects are allocated on the heap, and some of them are released, leading to potential memory fragmentation. Then, new objects with a minimum size greater than the new free chunks sizes are allocated.
\item \emph{LargeObjects:} Only large objects with a size greater than 65535 32-bit machines words are allocated on the heap. These objects are allocated directly in the old space.
\item \emph{Data0bjects:} The majority of the objects that will be allocated on the heap will be Data objects, which will only contain one-byte-sized integers in this benchmark. Data Objects can contain integers, float or double: the garbage collector will not go through their slots in the marking phase.
\end{itemize}

@@

\paragraph{Set-up.}The Configurable Benchmark evaluation was performed on an Asus Zenbook running Ubuntu 18.04 LTS, with a 2.2 Ghz processor Intel Core i5, and 8 Gb of 1600MHz DDR3 RAM. The Linux VM was compiled using GCC version 5.4.0. The compiled VMs are 32 bit (x86) applications with 32-bit objects and pointers. \footnote{Spur uses a common object header for both 32-bit and 64-bit versions, so 32-bit objects still have a 64-bit header and are all aligned on a 64-bit boundary.}

>>>>

We built three benchmarks out of the potential configurations:
\begin{itemize}
\item \emph{FragmentedHeap:} First, objects are allocated on the heap, and some of them are released, leading to potential memory fragmentation. Then, new objects with a minimum size greater than the new free chunks sizes are allocated.
\item \emph{LargeObjects:} Only large objects with a size greater than 65535 32-bit machine words are allocated on the heap. These objects are allocated directly in the old space.
\item \emph{Data0bjects:} The majority of the objects that will be allocated on the heap will be Data objects, which will only contain one-byte-sized integers in this benchmark. Data Objects can contain integers, float or double: the garbage collector will not go through their slots in the marking phase.
\end{itemize}

@@

\paragraph{Set-up.}The Configurable Benchmark evaluation was performed on an Asus Zenbook running Ubuntu 18.04 LTS, with a 2.2 Ghz processor Intel Core i5, and 8 Gb of 1600MHz DDR3 RAM. The Linux VM was compiled using GCC version 5.4.0. The compiled VMs are 32-bit (x86) applications with 32-bit objects and pointers. \footnote{Spur uses a common object header for both 32-bit and 64-bit versions, so 32-bit objects still have a 64-bit header and are all aligned on a 64-bit boundary.}
